---
title: "Dictionary"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# List of functions
# General bits
1. help(topic) function enables you to describe the function
```{r}
help("mode")
````

2. ?topic Usually, a name or character string specifying the topic for which help is sought
```{r}
?mode
````

3. Is() function lists objects to be examined or defined
```{r}
ls()
````

4. dir() function - lists the files in a directory/folder

```{r}
dir()
````

5. list.files() function - List the Files in a Directory/Folder
```{r}
list.files()
````

# Input and Output

1. save() function - saves objects in R
```{r}
z<- 30
save("z", file = "zorenfile.txt")
````

2. load() function reloads saved datasets
```{r}
load(file = "zorenfile.txt")
````
3. data() function Loads specified data sets, or list the available data sets.
```{r}
data(lib.loc = NULL)
````

4. library() function Loads/Attaches and Listsing of Packages
```{r}
library(lib.loc = NULL)
````

5. read.table() function Reads a file in table format and creates a data frame from it, with cases corresponding to lines and variables to fields in the file.
```{r}
apple <- read.table("Dictionary function.txt")
apple

````
6. read.csv() function Reads a file in table format and creates a data frame from it, with cases corresponding to lines and variables to fields in the file.
```{r}
read.csv("input output.csv")

````
7. scan() function reads data into a vector or list from the console or file
```{r}
scan ("numbers.txt")

````
8. print() function prints its argument and returns it 
```{r}
print("whats up")
````
9. cat() function concatenates and prints
```{r}
cat("whats up","duck")
````

10. write.table() making a document 

```{r}
write.table(c(1,2,3,4,5),"numbers.txt")
````










# Data Creation

1. c() function Combines Values into a Vector or List
```{r}
c(1,2,3,4,5)

````

2. from:to function -  (where from and to are replaced with numbers, e.g. 1:10)

```{r}
10:100


````
```{r}
100:50


````
3. seq() function 
```{r}
seq(1,100,3)


````

4. rep() function replicates elements of vectors and lists
```{r}
rep("programing",3)


````

5. data.frame() function creates data frames, tightly coupled collections of variables
```{r}
data.frame(2,2,3,3,4,4)


````
```{r}
data.frame(c(2,2,3,3,4,4),c(5,5,6,6,7,7))


````

6. list() function  constructs vector of vectors
```{r}
list(c(2,2,3,3,4,4),c(5,5,6,6,7,7))


````

7. matrix() function matrix creates a matrix from the given set of values.
```{r}
matrix(c(2,2,3,3,4,4))


````

8. factor() function
```{r}
factor(numbers<-c(2,2,3,3,4,4))


````

9. rbind() function combines R Objects by Rows 
```{r}
rbind(c(2,2,3,3,4,4),c(1,1,1,1,1,1))


````




10. cbind() function combines objects by columns
```{r}
cbind(c(2,2,3,3,4,4),c(9,9,9,9,9,9))


````













