---
title: "Dictionary"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# List of functions
# General bits
1. help(topic) function enables you to describe the function
```{r}
help("mode")
````

2. ?topic Usually, a name or character string specifying the topic for which help is sought
```{r}
?mode
````

3. Is() function lists objects to be examined or defined
```{r}
ls()
````

4. dir() function - lists the files in a directory/folder

```{r}
dir()
````

5. list.files() function - List the Files in a Directory/Folder
```{r}
list.files()
````

# Input and Output

1. save() function - saves objects in R
```{r}
z<- 30
save("z", file = "zorenfile.txt")
````

2. load() function reloads saved datasets
```{r}
load(file = "zorenfile.txt")
````
3. data() function Loads specified data sets, or list the available data sets.
```{r}
data(list = character())
````

4. library() function Loads/Attaches and Listsing of Packages
```{r}
library(lib.loc = NULL)
````








