
# "psych" Package

## Procedures for Psychological, Psychometric, and Personality Research

## Introduction

A sim.anova is a simulation function that falls under an all incompasing package called "psych." The sim.anova function enables one to simulate a three way ANOVA and generate a matrix design which will include three independent variables (independent variable 1,2 and 3). The simulated independent variables can have different number of levels as well as effect sizes for every main effect as well as interaction. The sim.anova function can also simulate one or multiple dependent variables. Since psychological research requires lots of time as well as resources, the sim.anova function is a very useful tool that enables a researcher to simulate and inspect data prior to conducting an actual experiment. In this tutorial I will demonstrate how to generate an analysis of variance with three independent variables, I will also demonstrate how to produce an output of an ANOVA table, and lastly how to use a ggplot2 package to plot the means. 



 For more information, see the <https://personalityproject.org/r> web page

## Functions for generating simulated data




### Creating simulated data for three way ANOVA

The fist step in creating a simulated data for 3-way ANOVA is to create a data frame function (data.df), this is where your sim.anova function will be placed (data.df <- sim.anova(). Since the sim.anova function can contain different arguments such as effect size as well as different levels of independent variables, firs lets identify these different arguments. The effect sizes are identified as "es1" "es2" and es3 for the effect size of the first, second and third  independent variable. The argument n stands for the sample size in each cell. The argument n1, n2 and n3 stand for numbers of levels in the independent variables one, two and three. By default the sim.anova function sets the effect sizes to zero, and levels in each independent variables to 2. 

# install.package("psych")
```{r}
data.df <- sim.anova(es1=.5, es2=1, es3=2, n3=3)  # 1st section of code
describe(data.df)

```
In the above example we are demonstrating that all of the rows, which measure a distinct variable with its corresponding value, belong to 1 subject (i.e. 1). This format is useful for analysis of repeated measures experiments in which the same subject may be asked about different benchmarks during the course of the experiment.

### create a table

###  Details 

```{r}
describe(data.df)[,3]
```

```{r}
means_variable <- describe(data.df)[,3]
```


```{r}
library(ggplot2)
means_variable <- as.data.frame(means_variable)
Means <- means_variable
ind_vars <- (IV1*)
ggplot(means_variable,aes(x = Means, y = ind_vars))+ 
  geom_point() 
```


```{r}
library(ggplot2)
Names <-rep(c("Dara", "Azalea", "Barbi", "Rowena", "Fiona"),each=2)
MF <- rnorm(10,45,25) # 10 is the number of numbers you want, and 45 to 25 is the range
Condition <- rep(c("Social","NonSocial"),5)
Aversity <- rep(c("A","N_A" ),times=c(4,6))
  plot_df <- data.frame(Names, MF, Condition, Aversity)
  
  ggplot(plot_df, aes(x=Condition, y=MF, group=Names, linetype=Aversity))+
    geom_line()+
    geom_text(label=Names)+
    theme_classic()

```


```{r}
library(ggplot2)
indep_var <- rep(as.factor(c("IV1","IV2","IV3"))) # this 2 means repeat ABC twice
iv_means <- c(1.5,1.5,2)

plot_df <- data.frame(indep_var,
                  
                      iv_means)

# basic bar graph

ggplot(plot_df, aes(x=indep_var,y=iv_means, # aestetics definition has gotten 
                   # color=factor_two))+  # color here means the border collor
                   ))+
  geom_bar(stat="identity", 
           position="dodge",
           color="red")

```






### Let’s look at an example of simulated data below

First load the package “psych” through library() if you have not done so

```
set.seed(42) data.df <- sim.anova(es1=1,es2=.5,es13=1) # this piece of code is designed for one main effect and one 

interaction 

describe(data.df) pairs.panels(data.df) #show how the design variables are orthogonal 

# 
summary(lm(DV~IV1*IV2*IV3,data=data.df)) 

summary(aov(DV~IV1*IV2*IV3,data=data.df)) 

set.seed(42) 

# here we are demonstrating the effect of not centering the data on the regression 

data.df <- sim.anova(es1=1,es2=.5,es13=1,center=FALSE) # describe(data.df) 

# 

#this example is not correct, because the IVs are not centered summary(lm(DV~IV1*IV2*IV3,data=data.df)) 

summary(aov(DV~IV1*IV2*IV3,data=data.df)) #compare with the lm model 

#now inspect multiple levels and quadratic terms 

set.seed(42) 

data.df <- sim.anova(es1=1,es13=1,n2=3,n3=4,es22=1) 

summary(lm(DV~IV1*IV2*IV3,data=data.df)) 

summary(aov(DV~IV1*IV2*IV3,data=data.df)) 

pairs.panels(data.df) 

# 

data.df <- sim.anova(es1=1,es2=-.5,within=c(-1,0,1),n=10) pairs.panels(data.df)

```
## Citations

J. Cohen (1982) Set correlation as a general multivariate data-analytic method. Multivariate Behavioral Research, 17(3):301-341.

J. Cohen, P. Cohen, S.G. West, and L.S. Aiken. (2003) Applied multiple regression/correlation analysis for the behavioral sciences. L. Erlbaum Associates, Mahwah, N.J., 3rd ed edition.

H. Hotelling. (1936) Relations between two sets of variates. Biometrika 28(3/4):321-377. E.Cramer and W. A. Nicewander (1979) Some symmetric, invariant measures of multivariate association. Psychometrika, 44:43-54.

V. D. R. Guide Jr. and M. Ketokivim (2015) Notes from the Editors: Redefining some methodological criteria for the journal. Journal of Operations Management. 37. v-viii

```{r}
library(psych)
sim.anova(es1 = 0, n = 2,n1 = 2, 
    within=NULL,factors=TRUE,center = TRUE,std=TRUE)
```


```{r}
sim.anova(es1 = 0, es2 = 0, es3 = 0, es12 = 0, es13 = 0,
    es23 = 0, es123 = 0, es11=0,es22=0, es33=0,n = 2,n1 = 2, n2 = 2, n3 = 2, 
    within=NULL,r=.8,factors=TRUE,center = TRUE,std=TRUE)
```




```{r}
summary(aov(DV~IV1*IV2*IV3,data=data.df)) #compare with the lm model

```


```{r}
library(ggplot2)
ggplot(data.df)
ggplot(data = data.df, aes(", n, ")) 
  
```






```{r}
data.df <- sim.anova(es1=1, es2 = .5, es13 = 1)  # one main effect and one interaction
describe(data.df)
pairs.panels(data.df)
summary(aov(DV~IV1*IV2*IV3,data=data.df)) #compare with the lm model

```

```{r}
data.df <- sim.anova(es1=1, es2 = .5, es13 = 1)  # one main effect and one interaction
describe(data.df)
pairs.panels(data.df)
summary(lm(DV~IV1*IV2*IV3,data=data.df))

summary(aov(DV~IV1*IV2*IV3,data=data.df)) #compare with the lm model

```





```{r}
data.df <- sim.anova(es1=1, es2 = .5, es123 = 1)  # one main effect and one interaction
describe(data.df)
pairs.panels(data.df)
```

```{r}
data.df <- sim.anova(es1=1, es2 = .5, es123 = 1, n=5, n1=2, n2=2, n3=2)  # one main effect and one interaction
describe(data.df)
pairs.panels(data.df)
```



```{r}
data.df <- sim.anova(es1=1, es2 = .5, es123 = 1, within=c(-1,0,1),n=10) # one main effect and one interaction
describe(data.df)
pairs.panels(data.df)

```

```{r}
summary(aov(DV~IV1*IV2*IV3,data=data.df))

summary(aov(DV~IV1*IV2*IV3,data=data.df)) #compare with the lm model

```


