---
title: "Journal"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


### problem 1

Do simple math with numbers, addition, subtraction, multiplication, division

```{r}
#List of computations
3+2
1+2
3-2
4*6
5/3
(1+6+4)/5

```


# problem 2

put numbers into variables, do simple math on the variables

```{r}

zoren <- 1
abc <- 2
zoren + abc

x <- c(1,2,3)
y <- c(5,6,7)

x+y
x*y
x/y

```

# problem 3
a code that will put numbers form 1 to a 100 in a variable using for loop 

```{r}

z<- length(100) # start with an empty length variable and then plug in 100 into it
for (x in 1:100){
  z[x] <- x
}
print(z)
```
Same code using a seq function
```{r}
z<- seq(1,100,1)
print(z)
```
# problem 4
here I am finding a sum from 1 to 100

```{r}
sum(1:100)

```

# problem 5
Writing a function to find the sum of all integers between any two intergers.
```{r}
func_addingintergers <- function(a,b) {
  return(sum(seq(a,b,1)))
  
}

func_addingintergers(1,10)
func_addingintergers(87,90)
```
# problem 6
listing only odd numbers from 1 to 100

Same code using a seq function
```{r}
z<- seq(1,100,2)
print(z)
```











