---
title: "Journal"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


### problem 1

Do simple math with numbers, addition, subtraction, multiplication, division

```{r}
#List of computations
3+2
1+2
3-2
4*6
5/3
(1+6+4)/5

```


# problem 2

put numbers into variables, do simple math on the variables

```{r}

zoren <- 1
abc <- 2
zoren + abc

x <- c(1,2,3)
y <- c(5,6,7)

x+y
x*y
x/y

```

# problem 3
a code that will put numbers form 1 to a 100 in a variable using for loop 

```{r}

z<- length(100) # start with an empty length variable and then plug in 100 into it
for (x in 1:100){
  z[x] <- x
}
print(z)
```
Same code using a seq function
```{r}
z<- seq(1,100,1)
print(z)
```
# problem 4
here I am finding a sum from 1 to 100

```{r}
sum(1:100)

```

# problem 5
Writing a function to find the sum of all integers between any two intergers.
```{r}
func_addingintergers <- function(a,b) {
  return(sum(seq(a,b,1)))
  
}

func_addingintergers(1,10)
func_addingintergers(87,90)
```
# problem 6
listing only odd numbers from 1 to 100

Same code using a seq function
```{r}
z<- seq(1,100,2)
print(z)
```
# going over a lesson on 2/4/2019
```{r}
a<- 1
b<-"Hello World"
d<-"3"
print(a)

class(d)

vector<- c(1,2,3,4,5,6,7,8)
vector[2:4]
vector[c(2,2,2,2,2)]
vector[vector <6] # show the numbers less than 7
vector[vector>=6] # greater or equal to 6
vector[vector!=4] # show numbers that are not 5

vector[8]<-3000 # put 3000 in the place of 8th number
vector

vector[1:2] <- 10

class(vector)
vector[7]<- "j" # put a number in the 7th place in the vector

vector

a<-c("1","2","3")
class(a)
b<- a
class(b)
as.numeric(b) # store charecters 123 as a number

a<- "ljjasjdflsjasf;lasdjflk;asdjfl;asdjfl"
strsplit(a,split="") # if you had a paragraph and you wanted to split the paragraph or put a period in R

a[1]

b[(1)][5]

example_list <- list(a=11, b=4, d=c(1,2,3,4))
example_list


data.frame() # particular way of structuring data


f<- matrix(0,nrow = 5, ncol = 3) # creating 5 rows and 3 columns

first_names <- c("asdf", "Asdfasd","asdfasdf")
ages<-c(3343,23122,67456)
grades<-c(89,56,99)

everybody <- data.frame(first_names,ages,grades)

everybody$ages[2] <- 12
```

# promblem 7
Generating prime numbers from a list of numbers from 1 to 1000

```{r}
x <- seq(1:1000)
y <- (0)
for (i in 2:999) {
  y<- c(x[y<=i],x[x>i & x%% i >0])
  x<-y
}
y

```

# Problem 8
Generating random numbers from 1 to 100

```{r}
sample(1:100, 100, replace = T) 

```


# problem 9

```{r}
sample(1:100, 25, replace = T) 

```

# problem 10a

```{r}
z<-c(10,11,12,13,14,15,16,17,18,19)
mean_zoren <- function(x) {
  mean_func <-0 # I need to initialize something if I want to use it in something else
  for (i in 1:length(x)) {
    mean_func<-mean_func + x[i]
    
  }
  mean_func<- mean_func/length(x)
    return(mean_func)
  }
mean_zoren(z)
```
# problem 10b
writing my own function for the mean

```{r}
mean_function <- function(z)
  return(sum(z)/length(z))
test_numbers<-c(4,30,12,10)
mean_function(test_numbers)

```

# problem 10c
finding median

```{r}
z<-c(5,6,7,8,9,10)
mode_function <- function(z) {
  while(length(z) > 2) {
    loc <- match(c(max(z),min(z)),z)
    z<-z[-loc]
  }
  if (length(z) == 2) {
     z <- (z[1]+z[2])/2
    }
  return(z)
}
mode_function (z)

  

```

# problem 10d
descriptive statistics - the range
```{r}
z<-c(20,21,22,23,24,25,26,27,28,29,30)
my_range<- function(z) {
  range_function <- max(z)-min(z)
  return(range_function) }
my_range(z)
  

```

# problem 10e
descriptive statistics - the standard deviation

```{r}
z<-c(20,21,22,23,24,25,26,27,28,29,30)
my_StandardDeviation<- function(z) {
  mean_function <- mean(z)
  var <- 0
  for (i in 1:length(z)){
    var<- var + (mean_function - x[i])^2
    var<- var/length(z)
    StDev <- sqrt(var)
    }
return(StDev)
my_StandardDeviation(z)
}
    
```

# problem 11
counting how many variables are in the string

```{r}
my_string <- "this one is not that bad"
nchar(my_string)

```

# problem 12
counting how many words are in the string
```{r}
my_string <- "this one is not that bad"
count_words <- length(strsplit(my_string,' ')[[1]])
print(count_words)
```

# problem 13
counting how many sentences are in the string
```{r}
my_string <- "This class is very hands on. You learn by practice. Looking forward to disecting more problems."
count_sentences <- length(strsplit(my_string,"\\.")[[1]])
print(count_sentences)
```

# problem 14
counting how many times a specific character occurs in a string

```{r}
my_string <- "one small step for man, one giant leap for mankind"
find <-"a"
count_character <- length(which(strsplit(my_string,"")[[1]]==find))
print(count_character)
```



# problem 15
logical test to see whether a word can be found within the text of another string

```{r}
mytest_word <- "the"
mytest_sentence <- "It is a nice day in the neighborhood"
mytest_word%in%mytest_sentence

```




# problem 16
Putting current computer time in milliseconds into a variable
```{r}
print(as.numeric(Sys.time())*1000, digits=15)
```

# problem 17
Measure how long a piece of code takes to run by measuring the time before the code is run, and after the code is run, and taking the difference to find the total time
```{r}
time_start <- as.numeric(Sys.time())
ed <- length(100)
for (i in 1:100) {
  ed[i] <- i
}
time_end <- as.numeric(Sys.time())
time_run <- time_end - time_start
print(time_run)
```

# problem 18
Readin a .txt file or .csv file into a variable

```{r}

```
