---
title: "Journal"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=FALSE)
```


### problem 1

Do simple math with numbers, addition, subtraction, multiplication, division

```{r}
#List of computations
3+2
1+2
3-2
4*6
5/3
(1+6+4)/5

```


# problem 2

put numbers into variables, do simple math on the variables

```{r}

zoren <- 1
abc <- 2
zoren + abc

x <- c(1,2,3)
y <- c(5,6,7)

x+y
x*y
x/y

```

# problem 3
a code that will put numbers form 1 to a 100 in a variable using for loop 

```{r}

z<- length(100) # start with an empty length variable and then plug in 100 into it
for (x in 1:100){
  z[x] <- x
}
print(z)
```
Same code using a seq function
```{r}
z<- seq(1,100,1)
print(z)
```
# problem 4
here I am finding a sum from 1 to 100

```{r}
sum(1:100)

```

# problem 5
Writing a function to find the sum of all integers between any two intergers.
```{r}
func_addingintergers <- function(a,b) {
  return(sum(seq(a,b,1)))
  
}

func_addingintergers(1,10)
func_addingintergers(87,90)
```
# problem 6
listing only odd numbers from 1 to 100

Same code using a seq function
```{r}
z<- seq(1,100,2)
print(z)
```
# going over a lesson on 2/4/2019
```{r}
a<- 1
b<-"Hello World"
d<-"3"
print(a)

class(d)

vector<- c(1,2,3,4,5,6,7,8)
vector[2:4]
vector[c(2,2,2,2,2)]
vector[vector <6] # show the numbers less than 7
vector[vector>=6] # greater or equal to 6
vector[vector!=4] # show numbers that are not 5

vector[8]<-3000 # put 3000 in the place of 8th number
vector

vector[1:2] <- 10

class(vector)
vector[7]<- "j" # put a number in the 7th place in the vector

vector

a<-c("1","2","3")
class(a)
b<- a
class(b)
as.numeric(b) # store charecters 123 as a number

a<- "ljjasjdflsjasf;lasdjflk;asdjfl;asdjfl"
strsplit(a,split="") # if you had a paragraph and you wanted to split the paragraph or put a period in R

a[1]

b[(1)][5]

example_list <- list(a=11, b=4, d=c(1,2,3,4))
example_list


data.frame() # particular way of structuring data


f<- matrix(0,nrow = 5, ncol = 3) # creating 5 rows and 3 columns

first_names <- c("asdf", "Asdfasd","asdfasdf")
ages<-c(3343,23122,67456)
grades<-c(89,56,99)

everybody <- data.frame(first_names,ages,grades)

everybody$ages[2] <- 12
```

# promblem 7
Generating prime numbers from a list of numbers from 1 to 1000

```{r}
x <- seq(1:1000)
y <- (0)
for (i in 2:999) {
  y<- c(x[y<=i],x[x>i & x%% i >0])
  x<-y
}
y

```

# Problem 8
Generating random numbers from 1 to 100

```{r}
sample(1:100, 100, replace = T) 

```


# problem 9

```{r}
sample(1:100, 25, replace = T) 

```

# problem 10a

```{r}
z<-c(10,11,12,13,14,15,16,17,18,19)
mean_zoren <- function(x) {
  mean_func <-0 # I need to initialize something if I want to use it in something else
  for (i in 1:length(x)) {
    mean_func<-mean_func + x[i]
    
  }
  mean_func<- mean_func/length(x)
    return(mean_func)
  }
mean_zoren(z)
```
# problem 10b
writing my own function for the mean

```{r}
mean_function <- function(z)
  return(sum(z)/length(z))
test_numbers<-c(4,30,12,10)
mean_function(test_numbers)

```

# problem 10c
finding median

```{r}
z<-c(5,6,7,8,9,10)
mode_function <- function(z) {
  while(length(z) > 2) {
    loc <- match(c(max(z),min(z)),z)
    z<-z[-loc]
  }
  if (length(z) == 2) {
     z <- (z[1]+z[2])/2
    }
  return(z)
}
mode_function (z)

  

```

# problem 10d
descriptive statistics - the range
```{r}
z<-c(20,21,22,23,24,25,26,27,28,29,30)
my_range<- function(z) {
  range_function <- max(z)-min(z)
  return(range_function) }
my_range(z)
  

```

# problem 10e
descriptive statistics - the standard deviation

```{r}
z<-c(20,21,22,23,24,25,26,27,28,29,30)
my_StandardDeviation<- function(z) {
  mean_function <- mean(z)
  var <- 0
  for (i in 1:length(z)){
    var<- var + (mean_function - x[i])^2
    var<- var/length(z)
    StDev <- sqrt(var)
    }
return(StDev)
my_StandardDeviation(z)
}
    
```

# problem 11
counting how many variables are in the string

```{r}
my_string <- "this one is not that bad"
nchar(my_string)

```

# problem 12
counting how many words are in the string
```{r}
my_string <- "this one is not that bad"
count_words <- length(strsplit(my_string,' ')[[1]])
print(count_words)
```

# problem 13
counting how many sentences are in the string
```{r}
my_string <- "This class is very hands on. You learn by practice. Looking forward to disecting more problems."
count_sentences <- length(strsplit(my_string,"\\.")[[1]])
print(count_sentences)
```

# problem 14
counting how many times a specific character occurs in a string

```{r}
my_string <- "one small step for man, one giant leap for mankind"
find <-"a"
count_character <- length(which(strsplit(my_string,"")[[1]]==find))
print(count_character)
```



# problem 15
logical test to see whether a word can be found within the text of another string

```{r}
mytest_word <- "the"
mytest_sentence <- "It is a nice day in the neighborhood" 
new_splitsentence <- strsplit(mytest_sentence," ")
mytest_word %in% new_splitsentence
```




# problem 16
Putting current computer time in milliseconds into a variable
```{r}
print(as.numeric(Sys.time())*1000, digits=15)
```

# problem 17
Measure how long a piece of code takes to run by measuring the time before the code is run, and after the code is run, and taking the difference to find the total time
```{r}
time_start <- as.numeric(Sys.time())
ed <- length(100)
for (i in 1:100) {
  ed[i] <- i
}
time_end <- as.numeric(Sys.time())
time_run <- time_end - time_start
print(time_run)
```

# problem 18
Readin a .txt file or .csv file into a variable

```{r}

```

# Harder Problems
# Problem 1. 
List the numbers from 1 to 100 with the following constraints. If the number can be divided by three evenly, then print Fizz instead of the number. If the number can be divided by five evenly, then print Buzz instead of the number. Finally, if the number can be divided by three and five evenly, then print FizzBuzz instead of the number
```{r, eval=FALSE}
numb <-(1:100)
  for (j in 1:length(numb)) {
  if(numb[j]%%3 == 0){
    numb[j] <-"Fizz"
  }
    
    
  }

```
```{r}
result <-1
for (j in 2:100){
  if(j %% 3 == 0){
    if (j %% 5 == 0) {
      result <-paste(result, "FizzBuzz", sep = ",") }
        else {result <- paste(result,"Fizz", sep = ", ")
    }
  }
  else if (j %% 5 == 0) {
    result <- paste(result, "Buzz", sep = ", ")
  }
  else {
    result <- paste(result, j, sep = ", ")
  }
}
print(result)

```

# Problem 2
Take text as input, and be able to produce a table that shows the counts for each character in the text
```{r}
z <-"lets see what happens"
table(unlist(strsplit(z,split="")))

```

```{r}
digits <- c(9,8,7,6,5,4,3,2,1)
letters <- c("a","s","d","j","k","l","m","n","o")
table <- data.frame(digits,letters)
print(table)
```

# Problem 3
Test the random number generator for a flat distribution. Generate a few million random numbers between 0 and 100. Count the number of 0s, 1s, 2s, 3s, etc. all the way up to 100. Look at the counts for each of the numbers and determine if they are relatively equal.
```{r}
z<-runif(20000000,0,100)
hist(z)
```

# Problem 4
Create a multiplication table Generate a matrix for a multiplication table. For example, the labels for the columns could be the numbers 1 to 10, and the labels for the rows could be the numbers 1 to 10. The contents of each of the cells in the matrix should be correct answer for multiplying the column value by the row value.
```{r}
z< c(1,2,3,4,5,6,7,8,9)
for(i in 1:2){
  for(j in 1:2){
    print(i*j)
  }
}

```

# Problem 5
Encrypt and Decrypt the Alphabet Turn any normal english text into an encrypted version of the text, and be able to turn any decrypted text back into normal english text.

```{r}
start_sequence <- c(99,399,130,140,550,20,20,30,20,40,50,2)
numbers <- unique(start_sequence)
scrambled_numbers <- sample(numbers)
encryption_key <- data.frame(numbers,scrambled_numbers)

encrypt_numbers <-function(input_sequence,key){
  encrypted_sequence<-c()
  for(i in 1:length(input_sequence)){
    original_number <- input_sequence[i]
    new_number <- key[key$numbers==original_number,]$scrambled_numbers
    encrypted_sequence[i] <- new_number
  }
  return(encrypted_sequence)
}

encrypt_numbers(start_sequence,encryption_key)


```

# Problem 6
Snakes and ladders
```{r}
tot_sum<-0 # this problem tells how many times you roll a dice to get sum total of the numbers to equal 100 or more
number_of_rolls<-0
while(tot_sum < 100){
  number_of_rolls <- number_of_rolls+1
  tot_sum <-tot_sum+sample(c(1,2,3,4,5,6),1)
}
number_of_rolls
```

multiple simulations recorded and saved
```{r}
save_rolls <- c()
for(sims in 1:100){
  total_sum<-0
  number_of_rolls<-0
  while(total_sum < 25){
    number_of_rolls <- number_of_rolls+1
    total_sum <-total_sum+sample(c(1,2,3,4,5,6),1)
  }
  save_rolls[sims] <- number_of_rolls
}
mean(save_rolls)
```
snakes and ladders
```{r}
snakesladders_board <- c(1,2,11,4,5,17,7,8,18,12,11,12,13,4,15,16,17,18,
              8,20,21,20,23,16,25,26,27,28,29,30,31,32)

run_game <- function(a_board){
  count <- 0
  position <- 1
  while(position < 25){
    count <- count+1
    position <- a_board[position+sample(seq(1,6),1)]
  }
  return(count)
}

mean(replicate(10000,run_game(snakesladders_board)))
```

# problem 7
Dice-rolling simulations. Assume that a pair of dice are rolled. Using monte carlo-simulation, compute the probabilities of rolling a 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, and 12, respectively


```{r}
calc_probability <- data.frame(c(2:12),replicate(11,0))
for (i in 1:1000) {
  roll <- sum(sample(1:6, 2, replace = TRUE))
  for (j in 2:12) {
    if (roll == j) {
      calc_probability[j-1,2] = calc_probability[j-1,2] + 1
    }
  }
}
calc_probability[,2] = calc_probability[,2]/1000
print(calc_probability)
```

# Problem 8

Monte Hall problem. The monte-hall problem is as follows. A contestant in a game show is presented with three closed doors. They are told that a prize is behind one door, and two goats are behind the other two doors. They are asked to choose which door contains the prize. After making their choice the game show host opens one of the remaining two doors (not chosen by the contestant), and reveals a goat. There are now two door remaining. The contestant is asked if they would like to switch their choice to the other door, or keep their initial choice. The correct answer is that the participant should switch their initial choice, and choose the other door. This will increase their odds of winning. Demonstrate by monte-carlo simulation that the odds of winning is higher if the participant switches than if the participants keeps their original choice
```{r}
doors<- c("A","B","C")
zdata= c()
for (i in 1:100) 
  {
  prize <- sample (doors) [1]
  pick <- sample (doors) [1]
  open <- sample (doors [which(doors !=pick & doors !=prize)]) [1] 
  switchyes <- doors[which(doors != pick & doors != open)]
  if(pick == prize) {zdata=c(zdata, "noswitchwin")}
  if(switchyes == prize) {zdata=c(zdata, "switchwin")}
  
  length(which(zdata == "switchwin"))
  length(which(zdata == "noswitchwin"))
  
}
```

# Problem 9
100 doors problem. Problem: You have 100 doors in a row that are all initially closed. You make 100 passes by the doors. The first time through, you visit every door and toggle the door (if the door is closed, you open it; if it is open, you close it). The second time you only visit every 2nd door (door 2, 4, 6, etc.). The third time, every 3rd door (door 3, 6, 9, etc.), etc, until you only visit the 100th door.
```{r, eval=F}

doors_puzzle <- function(ndoors=100,passes=100) {     
  doors <- rep(FALSE,ndoors)     
  for (ii in seq(1,passes)) {         
    mask <- seq(0,ndoors,ii)         
    doors[mask] <- !doors[mask]        }     
  return (which(doors == TRUE)) } doors_puzzle() 

```

```{r}

doors<-rep(0,100)

for(i in 1:100) {
  for(j in seq(i,100,by=i)){
    if(doors[j]==0){
      doors[j]<-1
      } else {
        doors[j]<-0
      }
    }
  }
doors

```

# Problem 10 
99 Bottles of Beer Problem In this puzzle, write code to print out the entire “99 bottles of beer on the wall”" song. For those who do not know the song, the lyrics follow this form:
X bottles of beer on the wall X bottles of beer Take one down, pass it around X-1 bottles of beer on the wall

Where X and X-1 are replaced by numbers of course, from 99 all the way down to 0
```{r}
z <- 99
first_sentence <- "bottles of beer on the wall,"
second_sentence <- "bottles of beer. Take one down, pass it around,"
third_sentence <- "bottles of beer on the wall!"
while (z > 0) {
  each_sentence <- paste(z,first_sentence,z,second_sentence,z-1,third_sentence)
  print(each_sentence)
  z = z -1
}

```





