---
title: "Notes"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# going over a lesson on 2/4/2019
```{r}
a<- 1
b<-"Hello World"
d<-"3"
print(a)

class(d)

vector<- c(1,2,3,4,5,6,7,8)
vector[2:4]
vector[c(2,2,2,2,2)]
vector[vector <6] # show the numbers less than 7
vector[vector>=6] # greater or equal to 6
vector[vector!=4] # show numbers that are not 5

vector[8]<-3000 # put 3000 in the place of 8th number
vector

vector[1:2] <- 10

class(vector)
vector[7]<- "j" # put a number in the 7th place in the vector

vector

a<-c("1","2","3")
class(a)
b<- a
class(b)
as.numeric(b) # store charecters 123 as a number

a<- "ljjasjdflsjasf;lasdjflk;asdjfl;asdjfl"
strsplit(a,split="") # if you had a paragraph and you wanted to split the paragraph or put a period in R

a[1]

b[(1)][5]

example_list <- list(a=11, b=4, d=c(1,2,3,4))
example_list


data.frame() # particular way of structuring data


f<- matrix(0,nrow = 5, ncol = 3) # creating 5 rows and 3 columns

first_names <- c("asdf", "Asdfasd","asdfasdf")
ages<-c(3343,23122,67456)
grades<-c(89,56,99)

everybody <- data.frame(first_names,ages,grades)

everybody$ages[2] <- 12
```

```{r}
data1 <- c(1,2,3)
data1[1]
data1[-1]

```

# 2/11/2019 3rd lecture
Downloading R repository

on February 25th we will talk about data analysis 
assignment 3 (R Basics) - R package assignment - how R code works, how it is shared
I will be submiting a link to a new R repository
R functions are prepackaged - in Packages - collect functions you have worked on

click instal tab in packages - repository cran allows y ou to save on cloud - choose your package and install
next step load the package - click the package button


# creating a simple function of adding 1 to whatever number you indicated
'''
my_function<- function(input){
  #body of code
return(output)
}
'''
```{r}
add_one <- function(x){
  return(x+1)
}
  add_one(9)


```

'''
{r, eval=FALSE}
add_one <- function(x){
# add one tox, and save the output
save_result <- x+1


another way to do it
'''
{r}
add_one <- function(x) return(x+1)
'''
```{r}
add_one <- function(x) return(x+1)

  add_one(7)


```

# how can we roll a die and get a number
'''
{r}
sample(1:6,1)
roll_dice <- function(){
return(sample(1:6,1))
}
roll_dice() # make sure you put something in the parenthesis
'''
```{r}
roll_dice <- function(x){
  return(sample(1:6,1))

}
  roll_dice()

```

creating a sum function 
```{r}
x <- c(1,2,3)
my_sum <- function(x){  # this is declaring a funtion
  get_sum<-sum(x)
  return(get_sum)
}
# to declare a variable
  a <- c(1,2,3)
```
# find a mean of restricted range of numbers
```{r}
ranged_mean  <- function(x, min_val, max_val){
  restricted_values <- x[x>min_val & x < max_val]
  return(mean(restricted_values))

}
  some_numbers <-c(3,4,3,2,3,4,5,6,7,8,8,8,9,8)
  ranged_mean(some_numbers,3,9)

```

```{r, eval=F}
ranged_mean  <- function(x, min_val, max_val){
  restricted_values <- x[x>min_val & x < max_val]
  outputs <- list(original_values = x, 
                  restricted_values=restricted_values
                  restricted_mean = mean(restricted_values)

}
  some_numbers <-c(3,4,3,2,3,4,5,6,7,8,8,8,9,8)
  ranged_mean(some_numbers,2,4)

```


# how to make new R project

steps
1. 
2.
3.


